Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
TypeResults

\subsection{The corpus}\label{chap:corpus}
For our experiments we use a large corpus of open source projects~\cite{githubCorpus2013}. This corpus has been assembled to contain relatively higher quality projects. Also, any duplicate projects were removed from this corpus. This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on. We filtered this corpus further to only include projects that use Maven, which is a build tool which is mainly used to manage dependencies in the Java ecosystem. We then filtered the corpus further to only include projects for which all external dependencies are available.

@@

>>>>

\subsection{The corpus}\label{chap:corpus}
For our experiments we use a large corpus of open source projects~\cite{githubCorpus2013}. This corpus has been assembled to contain relatively higher quality projects. Also, any duplicate projects were removed from this corpus. This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on. We filtered this corpus further to only include projects that use Maven, which is a build tool which is mainly used to manage dependencies in the Java ecosystem. We then filtered the corpus further to only include projects for which all external dependencies are available. This resulted in 1.343 projects of varying sizes averaging at 980 source lines of code (omitting whitespace, comments) per project.

@@

\subsection{Clone types}
In this chapter we display the differences between clone type 1-3 \cite{roy2007survey} and type 1R-3R as proposed in section \ref{sec:rtypes}. When running our clone detection script over the corpus, we get the results displayed in figure

\begin{figure}[H]
  \caption{Number of cloned declarations/statements.}
    \includegraphics[width=1\columnwidth]{img/TypeResults}
  \label{fig:tokenthreshold}
\end{figure}
